Congress text mining

### 2022-11-29 slides/slides.qmd
update

:::
## Data acquisition 3

```{.python }
@congress_deco(output_format='html')
def get_bill_text(query:str) -> str:

        hdr = {
                # specifying requested encoding
                'Cache-Control': 'no-cache',
                'charset': 'UTF-8',
                'User-Agent': random.choice(['Mozilla/5.0', 'Chrome 104.0.0.0', 
                                                'Chrome 52.0.2762.73', 'Chrome 55.0.2919.83'])
                }

        return (query, hdr)
```

@@

```{.python}
import plotly.ex

>>>>

:::

@@

```{.python}
import plotly.express as px
import pandas as pd

df = pd.read_csv("data\\data_28_11_sponsors.csv")
